Continuous Deductive Reasoning over Streamed RDF Data

### 2015-11-03 article.tex
refinement of the description of the Rete algorithm in reference to stream reasoning and semantics

  % Rete as non-streaming implementationexample (application to dataflow networks)
  Rete networks \citep{forgy79} are an example of production systems (a form of rule-based reasoning system) that are particularly suitable for extension with streaming semantics, being modelled as dataflow networks composed of incremental operators.
  These systems send data from operator to operator, with `memories' compiled for two-pass operators in which to retain the specific data received, in much the same way as sliding windows are used in stream processing.
  This makes them functionally similar to many stream-to-stream processing systems, and have even been a foundation for some such as Sparkwave \citep{sparkwave}.
  However, as \citep{forgy79} does not consider the semantics of stream processing, and those semantics are not clearly defined elsewhere for reasoning, such a semantics must still be defined before any stream reasoning system based on Rete may claim to adhere to them.

>>>>

  % Rete as non-streaming implementationexample (application to dataflow networks)
  Progressing from reasoning semantics to data processing, Rete networks \citep{forgy79} are an example of production systems (a form of rule-based reasoning system) that are particularly suitable for extension with streaming semantics, being modelled as dataflow networks composed of incremental operators.
  These systems send data from operator to operator, with `memories' compiled for two-pass operators in which to retain the specific data received, in much the same way as sliding windows are used in stream processing.
  This makes them functionally similar to many stream-to-stream processing systems, and they have even been a foundation for some such as Sparkwave \citep{sparkwave}.
  However, \citet{forgy79} did not incorporate the semantics of stream processing into the model underlying the Rete algorithm.
  In addition, more recent data-flow-based models either don't consider ``reasoning'' more expressive than RDFS \citep{sparkwave}, or are based on rule/query-level windowing \citep{C-SPARQL,walavalkar08streamingkb}, with problems as already discussed.
